\begin{thebibliography}{1}

\bibitem{} Bacon, P., Harb, J., and Precup, D. (2017). The Option-Critic Architecture. AAAI.

\bibitem{} Dayan, P. and Hinton, G. Feudal reinforcement learning. In NIPS. Morgan Kaufmann Publishers, 1993

\bibitem{} Machado MC, Bellemare MG, Bowling M. A Laplacian Framework for Option Discovery in
Reinforcement Learning. arXiv preprint arXiv:1703.00956. (2017) Mar 2.

\bibitem{} Richard S. Sutton, Doina Precup, Satinder Singh, Between MDPs and semi-MDPs: A framework for temporal abstraction in reinforcement learning, In Artificial Intelligence, Volume 112, Issues 1–2, 1999, Pages 181-211, ISSN 0004-3702, https://doi.org/10.1016/S0004-3702(99)00052-1.

\bibitem{} Sutton, R., Modayil, J., Delp, M., Degris, T., Pilarski, P., White, A., and Precup, D. (2011).
Horde: A scalable real-time architecture for learning knowledge from unsupervised
sensorimotor interaction. In Proceedings of the 10th International Conference on Autonomous
Agents and Multiagents Systems (AAMAS).

\bibitem{} Van Seijen, H., Fatemi, M., Romoff, J., Laroche, R., Barnes, T., and Tsang, J. (2017, June 13). Hybrid Reward Architecture for Reinforcement Learning. arXiv.org.

\bibitem{} Vezhnevets, A.S., Osindero, S., Schaul, T., Heess, N., Jaderberg, M., Silver, D., and Kavukcuoglu, K. (2017).
Feudal networks for hierarchical reinforcement learning. arXiv preprint arXiv:1703.01161

\bibitem{} Tessler, Chen, Givony, Shahar, Zahavy, Tom, Mankowitz,
Daniel J, and Mannor, Shie (2016).
A Deep Hierarchical Approach To Lifelong Learning In Minecraft. arXiv preprint arXiv:1604.07255

\bibitem{} Parr, Ronald and Russell, Stuart (1998). Reinforcement learning
With Hierarchies Of Machines. NIPS.

\bibitem{} Kaelbling, Leslie Pack (2014). Hierarchical learning in stochastic
domains: Preliminary results. ICML.

\end{thebibliography}